Magnetised Polish doughnuts revisited

### 2017-11-14 magnetised_polish_doughnuts_revisited/paper_revised_v2/referee_reply.txt

Referee Report

The authors have followed carefully all of the suggestions made and I am
pleased to see that they were able to provide more rigorous support to
some of the arguments presented in the paper. The new appendices A and B
present valuable additions to the paper.

In view of these considerations I am glad to recommend the publication of
the manuscript as a regular paper on A&A. At the same time, I'd like the
authors to consider some of the small suggestions listed below and
addressing some of the questions raised.

## A. ...We have included the following comment at the end of the paragraph
## following Eq. (27): "We note that the fluid enthalpy w includes the
## rest-mass density rhos, and can thus be defined as w = rho h where h
## is the specific enthalpy. The relativistic definition of this quantity
## is h = 1+epsilon+p/rho, where epsilon is the specific internal
## energy. From a thermodynamical point of view a non-relativistic fluid
## satisfies h = 1. Therefore, since we use poytropic equations of state
## (relating p with either w or rho in the same functional form) we are
## implictly assuming that h = 1, i.e. the discs we build in our
## procedure are non-relativistic from a thermodynamical point of view."

The authors should note that "w" is the *enthalpy density* and not the
enthalpy. This becomes clear: any "specific" quantity becomes a
"density" when multiplied by a rest-mass density.

## A: The reason we show the middle panel in logarithm scale and the
## right panel in linear scale is because this is the choice in
## Komissarov (2006). We have followed the same choice in order to
## facilitate the qualitative and quantitative comparison for this
## constant angular momentum test. If the referee concurred, we would
## prefer to keep the right panel in linear scale. If not, we would not
## mind changing the right panel to logarithmic scale.

Following too closely the work of Komissarov is not necessary and not
necessarily a good idea. Rather, I think that a plot in logarithmic
scale would be more informative.

## A: We have built models with very small values of beta_mc, such as
## beta_mc = 1e-20 (extremely high magnetisation) without encountering
## numerical difficulties. In practice we have found that there are no
## qualitative differences in the structure of the discs once beta_mc
## becomes smaller than a sufficiently small value...

It is important to incorporate this comment in the revised version.

## R: - Fig. 2: all of the panels would benefit from a legend showing the
## corresponding values of gamma and beta. This would avoid having to read
## the caption repeatedly. The same is true also for Fig. 3.
##
## A: Done.

I think that the legend should also report the value of the
black-hole's spin as this makes the various panels readable also
without having to consult the caption.

## If the referee considered these explanations satisfactory and would
## like to have them included in the manuscript, we would be happy to do
## so.

I find the explanation satisfactory and, as mentioned above, I find
Appendix B a nice addition to the paper.

### 2017-11-14 magnetised_polish_doughnuts_revisited/paper_lang_rev/paper_lang_rev.tex
new paper added

To construct our models of magnetised discs we follow the approach described in \citet{Qian:2009}. First, we find the radial location of the cusp and of the centre of the disc in the equatorial plane, $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$, defined as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
Next, we compute the partial derivatives of the potential, Eq.~\eqref{eq:potential}
\begin{equation}\label{eq:radial_der_pot}
\partial_r W = \partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\,,
\end{equation}
and
\begin{equation}\label{eq:polar_der_pot}
\partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}\,.
\end{equation}
Then, we integrate the radial partial derivative of the potential along the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ (assuming $W_{\mathrm{cusp}} = 0$) at the equatorial plane, thus obtaining the equatorial distribution of the potential between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$
\begin{equation}\label{eq:equatorial_pot}
W_{\mathrm{eq}}(r) = \int^{r_{\mathrm{c}}}_{r_{\mathrm{cusp}}}\left(\partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\right).
\end{equation}
Following~\citet{Qian:2009} (see also~\citet{Jaroszynski:1980}) we can divide equations \eqref{eq:radial_der_pot} and \eqref{eq:polar_der_pot} to obtain
\begin{equation}\label{eq:F}
F(r, \theta) = -\frac{\partial_r W}{\partial_{\theta} W} = \frac{\mathrm{d}\theta}{\mathrm{d}r}\,,
\end{equation}
where function $F(r, \theta)$ is known in closed form for the Kerr metric once an assumption for the angular momentum distribution has been made (cf.~Eq.~(\ref{eq:ansatz})). For this reason, Eq.~(\ref{eq:F}) also takes the form of an ordinary differential equation for the surfaces of constant potential, $\theta=\theta(r)$, which, upon integration, yields the location of those surfaces. \sg{We note} that in~\citet{Qian:2009} these are surfaces of constant {\it fluid pressure} instead, since their discs are purely hydrodynamical.

@@

Next, we choose all the initial radial values for the integration of Eq.~\eqref{eq:F} to lie between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$ ($\theta = \pi / 2$). Since we are only interested in the equipotential surfaces inside the Roche lobe of the disc, our choice of initial values provides us a mapping of the equipotential surfaces of the torus. Given that we have already obtained both the equipotential surfaces $\theta(r)$ which cross the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ at the equatorial plane and the values of the potential in that segment, we can obtain the complete potential distribution for the torus (outside of that segment). Once we have the potential distribution, we can find the fluid pressure at the centre of the disc from Eq.~\eqref{eq:enthalpy_eq},
\begin{equation}
p_{\mathrm{c}} = w_{\mathrm{c}}(W_{\mathrm{in}} - W_{\mathrm{c}})\left(\frac{\kappa}{\kappa - 1} + \frac{\lambda
}{\lambda
 - 1}\frac{1}{\beta_{\mathrm{m}_{\mathrm{c}}}}\right)^{-1},
\end{equation}
where $w_{\mathrm{c}}$ is the enthalpy density at the centre and
\begin{equation}
\label{eq:beta_eq}
\beta_{\mathrm{m}} = p/p_{\mathrm{m}},
\end{equation}
is the magnetisation parameter ($\beta_{\mathrm{m}_{\mathrm{c}}}$ being the magnetisation parameter at the centre of the disc). Using this definition, we can find the magnetic pressure at the centre,
\begin{equation}
p_{\mathrm{m_{\mathrm{c}}}} = p_{\mathrm{c}}/\beta_{\mathrm{m}_{\mathrm{c}}}\,.
\end{equation}
With both pressures known at the centre, fluid and magnetic, we can now find the constants $K$ and $K_{\mathrm{m}}$ using equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}. Therefore, for a given inner radius of the disc $r_{\mathrm{in}}$ we can obtain the potential $W_{\mathrm{in}}$. We now finally have all the ingredients required to find the enthalpy density distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the rest-mass density distribution, which can be trivially obtained inverting the barotropic relation, $p = K \rho^{\kappa}$. We note that the fluid enthalpy density $w$ includes the rest-mass density $\rho$, and can thus be defined as $w=\rho h$ where $h$ is the specific enthalpy. The relativistic definition of this quantity is $h=1+\varepsilon+p/\rho$, where $\varepsilon$ is
the specific internal energy. From a thermodynamical point of view a non-relativistic fluid satisfies $h=1$. Therefore,
since we use poytropic equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
implicitly assuming that $h=1$, \sg{that is,} the discs we build in our procedure are non-relativistic from a thermodynamical point of view.

For the integration of Eq.~\eqref{eq:equatorial_pot} we use the composite Simpson's rule. It is important to use a very small integration step because the slope is very steep. In this work, we use a step $\Delta r = 10^{-6}$. Using the analytic, constant angular momentum case for comparison, we tested that 
a larger value of $\Delta r$ gives unacceptable accuracy losses. On the other hand, to integrate the ordinary differential equation \eqref{eq:F} we use a fourth-order Runge-Kutta method. Again, it is also important here to choose a suitable step of integration, especially at the outer end of the disc, because Eq.~\eqref{eq:F} diverges at the equatorial plane (the equipotential surfaces cross the equatorial plane perpendicularly). We show the proof of this statment in Appendix~\ref{div_partial_W}.

@@

To reduce the number of free parameters to build the initial models we do as in~\citet{Komissarov:2006} and fix the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the enthalpy density at the disc centre, $w_{\mathrm{c}}$. More precisely, we choose $\kappa = \lambda = 4/3$ and $w_{\mathrm{c}} = 1$. This still leaves us with five parameters to control the size, shape, thickness, and magnetisation of the disc, namely the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$, and the inner radius of the disc $r_{\mathrm{in}}$. We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models). We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as \sg{for example} $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties. No qualitative differences in the structure of the discs are found once $\beta_{\mathrm{m}_{\mathrm{c}}}$ becomes smaller than a sufficiently small value, about $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$. This is the reason why we choose that particular value as our lower limit in the figures and tables of the manuscript.

@@

A representative sample of the isodensity surfaces for some of our models appears in \sg{Fig.}~\ref{models}. We plot, in particular, the models of Table~\ref{table:3}, for which the magnetisation is highest ($\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$). From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that \sg{characterise} the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption of the figure).  A rapid inspection shows that the structure of the discs noticeable changes when the parameters change. Notice that the spatial scale in all of the plots of this figure has been chosen so as to facilitate the visualization of the discs (which can be fairly small in some cases) and, as such, is different in each plot. A typical Polish doughnut is represented by the model in the top-left panel. As the black hole spin increases, the discs are closer to the black hole and its relative size with respect to the black hole is smaller for all values of $\gamma$ and $\beta$. For $\gamma=0$ the discs are infinite, irrespective of the value of $a$ and $\beta$. As $\gamma$ and $\beta$ increase from 0 to 0.9 (compare the three top rows) the discs become significantly thinner and radially smaller (see also Fig.~\ref{more-profile} below). It is also interesting to note that the maximum value of the rest-mass density is higher (with respect to the value at the disc centre) as the spin increases.

@@

Figure~\ref{magnetisation} shows the effects of changing the parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$ (the magnetisation) in the structure of the discs. From left to right the values plotted in each panel are $\beta_{\mathrm{m}_{\mathrm{c}}}=10^3$, 1, and $10^{-3}$. The model chosen corresponds to $a=0.9$ and $\gamma=\beta=0.5$. The larger the value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ the less important the effects of the magnetisation in the disc structure. \sg{Fig.}~\ref{magnetisation} shows that, at least for the kind of magnetic field distribution we are considering, the effects of the magnetisation are minor. The disc structure remains fairly similar for all values of $\beta_{\mathrm{m}_{\mathrm{c}}}
$ and the only quantitative differences are found in the location of the centre of the disc (which moves inward with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$). This can be more clearly \sg{visualised} in \sg{Fig.}~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the rest-mass density for the same three cases plotted in Fig.~\ref{magnetisation}.

@@

In order to provide a quantitative comparison of the structural differences that appear along the sequence of equilibrium models, we plot in Fig.~\ref{max-vs-magnetisation} the variation of the maximum of the rest-mass density (left panel), the radial location of the maximum of the fluid pressure (middle panel), and the radial location of the maximum of the magnetic pressure (right panel) as a function of the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$. All quantities plotted are measured at the equatorial plane. \sg{Let us first consider the left panel. The line type used indicates the value of the black hole spin $a$, namely, a dotted line is for $a=0.5$, a dashed line for $a=0.9$, and a solid line for $a=0.99$. Correspondingly, the colour of the lines indicates the value of $\beta$ and $\gamma$ used, namely, red curves correspond to $\gamma=\beta=0$, the blue ones to $\gamma=\beta=0.5$, and the black ones to $\gamma=\beta=0.9$ \bf{Seg\'un lo que han dicho arriba, todo esto deber\'ia ser borrado.}}. All curves show the same monotonically decreasing trend with $\beta_{\mathrm{m}_{\mathrm{c}}}$, yet for small enough and large enough values of $\beta_{\mathrm{m}_{\mathrm{c}}} $ the value of the rest-mass density maximum does not change. However, in the interval $10^{-2}\le \beta_{\mathrm{m}_{\mathrm{c}}} \le 10^{2}$, $\rho_{\rm max}$ changes abruptly. The larger the black hole spin the larger the drop in the maximum of the rest-mass density. For sufficiently large values of $\beta_{\mathrm{m}_{\mathrm{c}}}$ (small magnetisation) the value of $\rho_{\rm max}$ stays constant to the same value irrespective of the black hole rotation.

>>>>

To construct our models of magnetised discs we \sg{have followed} the approach described in \citet{Qian:2009}. First, we find the radial location of the cusp and of the centre of the disc in the equatorial plane, $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$, defined as the solutions to the equation $l(r) - l_{\mathrm{K}} = 0$.
Next, we compute the partial derivatives of the potential, Eq.~\eqref{eq:potential}
\begin{equation}\label{eq:radial_der_pot}
\partial_r W = \partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\,,
\end{equation}
and
\begin{equation}\label{eq:polar_der_pot}
\partial_{\theta} W = \partial_{\theta} \ln|u_t| - \frac{\Omega \partial_{\theta}l}{1 - \Omega l}\,.
\end{equation}
Then, we integrate the radial partial derivative of the potential along the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ (assuming $W_{\mathrm{cusp}} = 0$) at the equatorial plane, thus obtaining the equatorial distribution of the potential between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$
\begin{equation}\label{eq:equatorial_pot}
W_{\mathrm{eq}}(r) = \int^{r_{\mathrm{c}}}_{r_{\mathrm{cusp}}}\left(\partial_r \ln|u_t| - \frac{\Omega \partial_rl}{1 - \Omega l}\right).
\end{equation}
Following~\citet{Qian:2009} (see also~\citet{Jaroszynski:1980}) we can divide equations \eqref{eq:radial_der_pot} and \eqref{eq:polar_der_pot} to obtain
\begin{equation}\label{eq:F}
F(r, \theta) = -\frac{\partial_r W}{\partial_{\theta} W} = \frac{\mathrm{d}\theta}{\mathrm{d}r}\,,
\end{equation}
where function $F(r, \theta)$ is known in closed form for the Kerr metric once an assumption for the angular momentum distribution has been made (cf.~Eq.~(\ref{eq:ansatz})). For this reason, Eq.~(\ref{eq:F}) also takes the form of an ordinary differential equation for the surfaces of constant potential, $\theta=\theta(r)$, which, upon integration, yields the location of those surfaces. \sg{We note} that in~\citet{Qian:2009} these are surfaces of constant {\it fluid pressure} instead, since their discs are purely hydrodynamical.

@@

Next, we choose all the initial radial values for the integration of Eq.~\eqref{eq:F} to lie between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$ ($\theta = \pi / 2$). Since we are only interested in the equipotential surfaces inside the Roche lobe of the disc, our choice of initial values provides us a mapping of the equipotential surfaces of the torus. Given that we have already obtained both the equipotential surfaces $\theta(r)$ which cross the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ at the equatorial plane and the values of the potential in that segment, we can obtain the complete potential distribution for the torus (outside of that segment). Once we have the potential distribution, we can find the fluid pressure at the centre of the disc from Eq.~\eqref{eq:enthalpy_eq},
\begin{equation}
p_{\mathrm{c}} = w_{\mathrm{c}}(W_{\mathrm{in}} - W_{\mathrm{c}})\left(\frac{\kappa}{\kappa - 1} + \frac{\lambda
}{\lambda
 - 1}\frac{1}{\beta_{\mathrm{m}_{\mathrm{c}}}}\right)^{-1},
\end{equation}
where $w_{\mathrm{c}}$ is the enthalpy density at the centre and
\begin{equation}
\label{eq:beta_eq}
\beta_{\mathrm{m}} = p/p_{\mathrm{m}},
\end{equation}
is the magnetisation parameter ($\beta_{\mathrm{m}_{\mathrm{c}}}$ being the magnetisation parameter at the centre of the disc). Using this definition, we can find the magnetic pressure at the centre,
\begin{equation}
p_{\mathrm{m_{\mathrm{c}}}} = p_{\mathrm{c}}/\beta_{\mathrm{m}_{\mathrm{c}}}\,.
\end{equation}
With both pressures known at the centre, fluid and magnetic, we can now find the constants $K$ and $K_{\mathrm{m}}$ using equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}. Therefore, for a given inner radius of the disc $r_{\mathrm{in}}$ we can obtain the potential $W_{\mathrm{in}}$. We now finally have all the ingredients required to find the enthalpy density distribution (Eq.~\eqref{eq:enthalpy_eq}), the fluid pressure and magnetic pressure distributions (Eqs.~\eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the rest-mass density distribution, which can be trivially obtained inverting the barotropic relation, $p = K \rho^{\kappa}$. We note that the fluid enthalpy density $w$ includes the rest-mass density $\rho$, and can thus be defined as $w=\rho h$ where $h$ is the specific enthalpy. The relativistic definition of this quantity is $h=1+\varepsilon+p/\rho$, where $\varepsilon$ is
the specific internal energy. From a thermodynamical point of view a non-relativistic fluid satisfies $h=1$. Therefore,
since we use \sg{polytropic} equations of state (relating $p$ with either $w$ or $\rho$ in the same functional form) we are
implicitly assuming that $h=1$, \sg{that is,} the discs we build in our procedure are non-relativistic from a thermodynamical point of view.

For the integration of Eq.~\eqref{eq:equatorial_pot} we \sg{have used} the composite Simpson's rule. It is important to use a very small integration step because the slope is very steep. In this work, we \sg{have used} a step $\Delta r = 10^{-6}$. Using the analytic, constant angular momentum case for comparison, we tested that 
a larger value of $\Delta r$ gives unacceptable accuracy losses. On the other hand, to integrate the ordinary differential equation \eqref{eq:F} we \sg{have employed} a fourth-order Runge-Kutta method. Again, it is also important here to choose a suitable step of integration, especially at the outer end of the disc, because Eq.~\eqref{eq:F} diverges at the equatorial plane (the equipotential surfaces cross the equatorial plane perpendicularly). We show the proof of this statment in Appendix~\ref{div_partial_W}.

@@

To reduce the number of free parameters to build the initial models we \sg{have done} as in~\citet{Komissarov:2006} and \sg{have fixed} the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the enthalpy density at the disc centre, $w_{\mathrm{c}}$. More precisely, we \sg{have chosen} $\kappa = \lambda = 4/3$ and $w_{\mathrm{c}} = 1$. This still leaves us with five parameters to control the size, shape, thickness, and magnetisation of the disc, namely the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$, and the inner radius of the disc $r_{\mathrm{in}}$. We \sg{have built} a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, \sg{that is,} models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, \sg{that is,} equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, \sg{that is,} highly-magnetised models). We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as \sg{for example} $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties. No qualitative differences in the structure of the discs are found once $\beta_{\mathrm{m}_{\mathrm{c}}}$ becomes smaller than a sufficiently small value, about $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$. This is the reason why we \sg{have chosen} that particular value as our lower limit in the figures and tables of the manuscript.

@@

A representative sample of the isodensity surfaces for some of our models appears in \sg{Fig.}~\ref{models}. We plot, in particular, the models of Table~\ref{table:3}, for which the magnetisation is highest ($\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$). From left to right the columns of this figure correspond to increasing values of the black hole spin, namely, $a=0.5$, 0.9 and 0.99, while from top to bottom the rows correspond to different combinations of the $\gamma$ and $\beta$ parameters that \sg{characterise} the ansatz for the angular momentum distribution of~\citet{Qian:2009} (the particular values are indicated in the caption \sg{and legends} of the figure).  A rapid inspection shows that the structure of the discs noticeable changes when the parameters change. Notice that the spatial scale in all of the plots of this figure has been chosen so as to facilitate the visualization of the discs (which can be fairly small in some cases) and, as such, is different in each plot. A typical Polish doughnut is represented by the model in the top-left panel. As the black hole spin increases, the discs are closer to the black hole and its relative size with respect to the black hole is smaller for all values of $\gamma$ and $\beta$. For $\gamma=0$ the discs are infinite, irrespective of the value of $a$ and $\beta$. As $\gamma$ and $\beta$ increase from 0 to 0.9 (compare the three top rows) the discs become significantly thinner and radially smaller (see also Fig.~\ref{more-profile} below). It is also interesting to note that the maximum value of the rest-mass density is higher (with respect to the value at the disc centre) as the spin increases.

@@

\sg{Fig.}~\ref{magnetisation} shows the effects of changing the parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$ (the magnetisation) in the structure of the discs. From left to right the values plotted in each panel are $\beta_{\mathrm{m}_{\mathrm{c}}}=10^3$, 1, and $10^{-3}$. The model chosen corresponds to $a=0.9$ and $\gamma=\beta=0.5$. The larger the value of $\beta_{\mathrm{m}_{\mathrm{c}}}$ the less important the effects of the magnetisation in the disc structure. \sg{Fig.}~\ref{magnetisation} shows that, at least for the kind of magnetic field distribution we are considering, the effects of the magnetisation are minor. The disc structure remains fairly similar for all values of $\beta_{\mathrm{m}_{\mathrm{c}}}
$ and the only quantitative differences are found in the location of the centre of the disc (which moves inward with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$) and of the range of variation of the isodensity contours (the maximum being slightly larger with decreasing $\beta_{\mathrm{m}_{\mathrm{c}}}$). This can be more clearly \sg{visualised} in \sg{Fig.}~\ref{magnetisation-profile} which displays the radial profile at the equatorial plane of the rest-mass density for the same three cases plotted in Fig.~\ref{magnetisation}.

@@

In order to provide a quantitative comparison of the structural differences that appear along the sequence of equilibrium models, we plot in Fig.~\ref{max-vs-magnetisation} the variation of the maximum of the rest-mass density (left panel), the radial location of the maximum of the fluid pressure (middle panel), and the radial location of the maximum of the magnetic pressure (right panel) as a function of the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$. All quantities plotted are measured at the equatorial plane. \sg{Let us first consider the left panel. The line type used indicates the value of the black hole spin $a$, namely, a dotted line is for $a=0.5$, a dashed line for $a=0.9$, and a solid line for $a=0.99$. Correspondingly, the colour of the lines indicates the value of $\beta$ and $\gamma$ used, namely, red curves correspond to $\gamma=\beta=0$, the blue ones to $\gamma=\beta=0.5$, and the black ones to $\gamma=\beta=0.9$}. All curves show the same monotonically decreasing trend with $\beta_{\mathrm{m}_{\mathrm{c}}}$, yet for small enough and large enough values of $\beta_{\mathrm{m}_{\mathrm{c}}} $ the value of the rest-mass density maximum does not change. However, in the interval $10^{-2}\le \beta_{\mathrm{m}_{\mathrm{c}}} \le 10^{2}$, $\rho_{\rm max}$ changes abruptly. The larger the black hole spin the larger the drop in the maximum of the rest-mass density. For sufficiently large values of $\beta_{\mathrm{m}_{\mathrm{c}}}$ (small magnetisation) the value of $\rho_{\rm max}$ stays constant to the same value irrespective of the black hole rotation.
